---
title: "practica1"
author: "Jaime"
date: '2022-07-07'
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
- \usepackage[utf8]{inputenc}
- \usepackage{graphicx}
- \usepackage[labelfont=bf]{caption}
- \usepackage{longtable}
- \usepackage{float}
- \usepackage{fancyhdr}
- \usepackage{fancyheadings}
- \pagestyle{fancy}
- \lhead{\scriptsize Manual de R para el científico de datos}
- \chead{}
- \rhead{\scriptsize \leftmark}
- \lfoot{\textit{www.gritos.org}}
- \rfoot{\thepage}
documentclass: article
lang: es-ES
---
\newpage
\tableofcontents


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
mtcars[order(mtcars$gear,mtcars$mpg),]
```
# Jaime
```{r}
library(dplyr)
arrange(.data=mtcars,mtcars$gear,mtcars$mpg)
```
## isaac
### Pena
```{r}
small_mtcars <-
mtcars %>%
arrange(gear) %>%
slice(1:10)
small_mtcars
```
```{r}
library(ggplot2)
ggplot(mtcars, aes(x = wt, y = mpg)) +
geom_point() +
geom_smooth(method = lm)
```
```{r}
#install.packages("pacman")
library(pacman)
p_load(ggplot2, ggthemes, dplyr, readr)
```
```{r}
chilean_exports <- "year,product,export,percentage
2006,copper,4335009500,81
2006,others,1016726518,19
2007,copper,9005361914,86
2007,others,1523085299,14
2008,copper,6907056354,80
2008,others,1762684216,20
2009,copper,10529811075,81
2009,others,2464094241,19
2010,copper,14828284450,85
2010,others,2543015596,15
2011,copper,15291679086,82
2011,others,3447972354,18
2012,copper,14630686732,80
2012,others,3583968218,20
2013,copper,15244038840,79
2013,others,4051281128,21
2014,copper,14703374241,78
2014,others,4251484600,22
2015,copper,13155922363,78
2015,others,3667286912,22"
exports_data <- read_csv(chilean_exports)
```
```{r}
exports_data
```

```{r}
p1 <- ggplot(aes(y = export, x = year, colour = product), data = exports_data) +
geom_line()
p1
```
```{r}
library(reticulate)
```
```{r}
reticulate::conda_install(packages = "numpy")
```

```{python}
import numpy as np
```

```{r}
library(readxl)
CEP<-read_excel("D:/CEP_sep-oct_2017.xlsx",sheet=2)
head(CEP)

```
```{r}
library(dplyr)
CEP1=select(CEP,pond=POND,sexo=SEXO,
            region=REGION,edad=DS_P2_EXACTA,
           satisfaccion_vida=SV_1,satisfaccion_chilenos=SV_2,eval_econ=MB_P2 )
CEP1
```
```{r}
class(CEP1$sexo)
```
```{r}
table(CEP1$sexo)
```



```{r}
library(dplyr)
CEP2<-mutate(CEP1, sexo_chr = dplyr::recode(CEP1$sexo, '1' = "hombre", '2' = "mujer"))
table(CEP2$sexo_chr)
```

```{r}
CEP3 <- mutate(CEP2, sexo_factor = factor(CEP2$sexo, 
                                        labels = c("Hombre", "Mujer")))

```
```{r}
class(CEP3$sexo_factor)
```

```{r}
table(CEP3$region)
```
```{r}
library(knitr)
kable(table(CEP3$region))

```
```{r}
class(CEP3$region)
```
```{r}
library(car)
CEP <- mutate(CEP3, region_factor = car::recode(CEP3$region, "1:12 = 1; 13 = 2; 14:15 = 1"))

```
```{r}

```

```{r}
class(CEP$region_factor)
```
```{r}
library(VIM)
library(ggplot2)
head(msleep)
```

```{r}
newdata<-kNN(msleep,k=5)
head(newdata)
```
% Please add the following required packages to your document preamble:
% \usepackage{longtable}
% Note: It may be necessary to compile the document several times to get a multi-page table to line up properly
\begin{longtable}[c]{llllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllllll}
VOTACION\_1 & VOTACION\_2 & VOTACION\_3 & VOTACION\_4 & SV\_1 & SV\_2 & MB\_P1\_1 & MB\_P1\_2 & MB\_P1\_3 & MB\_P2 & MB\_P3 & MB\_P4 & MB\_P5 & MB\_P6 & MB\_P7 & MB\_P8 & MB\_P9 & MB\_P10 & MB\_P11 & MB\_P12 & MB\_P12A & MB\_P13 & MB\_P13A & MB\_P14 & MB\_P14A & MB\_P15\_A & MB\_P15\_B & MB\_P15\_C & MB\_P15\_D & MB\_P15\_E & MB\_P15\_F & MB\_P15\_G & MB\_P15\_H & MB\_P15\_I & MB\_P15\_J & MB\_P15\_K & MB\_P15\_L & MB\_P15\_M & MB\_P15\_N & MB\_P15\_O & MB\_P15\_P & MB\_P15\_Q & MB\_P15\_R & MB\_P15\_S & MB\_P15\_T & MB\_P15\_U & MB\_P15\_V & MB\_P15\_W & MB\_P15\_X & MB\_P15\_Y & MB\_P15\_Z & MB\_P16 & MB\_P17 & MB\_P18 & ELE\_1 & ELE\_2 & ELE\_3 & ELE\_4 & ELE\_5 & ELE\_6\_1 & ELE\_6\_2 & ELE\_6\_3 & ELE\_6\_4 & ELE\_6\_5 & ELE\_6\_6 & ELE\_6\_7 & PE\_E0 & MEP\_1 & MEP\_2 & MEP\_3 & MEP\_4 & MEP\_5\_1 & MEP\_5\_2 & MEP\_5\_3 & MEP\_5\_4 & MEP\_5\_5 & MEP\_5\_6 & MEP\_5\_7 & MEP\_5\_8 & MEP\_6 & MEP\_7 & MEP\_8 & MEP\_9\_1 & MEP\_9\_2 & MEP\_9\_3 & MEP\_9\_4 & MEP\_9\_5 & MEP\_9\_6 & MEP\_10\_1 & MEP\_10\_2 & DPP\_1 & DPP\_2 & DPP\_3\_1 & DPP\_3\_2 & DPP\_3\_3 & DPP\_4 & DPP\_5A & DPP\_5B & DPP\_5C & DPP\_6A & DPP\_6B & DPP\_6C & DPP\_7A & DPP\_7B & DPP\_7C & DPP\_8A & DPP\_8B & DPP\_8C & DPP\_9A & DPP\_9B & DPP\_9C & DPP\_10A & DPP\_10B & DPP\_10C & DPP\_11 & DPP\_12A & DPP\_12B & DPP\_12C & DPP\_13A & DPP\_13B & DPP\_13C & DPP\_14 & DPP\_15A & DPP\_15B & DPP\_15C & DPP\_16A & DPP\_16B & DPP\_16C & DPP\_16D & DPP\_17A & DPP\_17B & DPP\_17C & DPP\_17D & DPP\_18A & DPP\_18B & DPP\_18C & DPP\_18D & DPP\_19A & DPP\_19B & DPP\_19C & DPP\_19D & DPP\_20\_1 & DPP\_20\_2 & DPP\_20\_3 & DPP\_20\_4 & DPP\_20\_5 & DPP\_20\_6 & DPP\_20\_7 & DPP\_20\_8 & DPP\_21\_1 & DPP\_21\_2 & DPP\_21\_3 & DPP\_21\_4 & DPP\_22\_1 & DPP\_22\_2 & DPP\_23\_1 & DPP\_23\_2 & DPP\_23\_3 & DPP\_23\_4 & DPP\_23\_5 & DPP\_23\_6 & DPP\_23\_7 & DS\_P1 & DS\_P2 & DS\_P2\_EXACTA & DS\_P2A\_DIA & DS\_P2A\_MES & DS\_P2A\_ANO & DS\_P3 & DS\_P4 & DS\_P5 & DS\_P6 & DS\_P7 & DS\_P8 & DS\_P9 & DS\_P10 & DS\_P10\_OTRA & DS\_P11 & DS\_P12 & DS\_P13 & DS\_P14A & DS\_P14A\_EXACTA & DS\_P14B & DS\_P14B\_EXACTA & DS\_P14C & DS\_P14C\_EXACTA & DS\_P15 & DS\_P16 & DS\_P17 & DS\_P18 & DS\_P19 & DS\_P20\_1 & DS\_P20\_2 & DS\_P20\_3 & DS\_P20\_4 & DS\_P20\_5 & DS\_P20\_6 & DS\_P20\_7 & DS\_P20\_8 & DS\_P20\_9 & DS\_P20\_10 & DS\_P20\_11 & DS\_P20\_12 & DS\_P20\_13 & DS\_P20\_14 & DS\_P20\_15 & DS\_P20\_16 & DS\_P20\_17 & DS\_P21\_1 & DS\_P21\_2 & NOM\_COMUNA & SEXO & EDAD\_REC & REGION & POND & ZONA\_U\_R & GSE\_REC & DPP\_11\_REC & ANOS\_REC & REGION\_REC \\
\endfirsthead
%
\endhead
%
10 & 4 & 4 & 4 & 8 & 3 & 3 & 5 & 7 & 1 & 3 & 4 & 2 & 2 & 3 & 2 & 8 & 2 & 2 & 7 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 3 & 1 & 1 & 1 & 1 & 3 & 3 & 3 & 2 & 9 & 2 & 2 & 2 & 2 & 3 & 2 & 3 & 2 & 3 & 3 & 8 & 23 & 7 & 10 & 88 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 3 & 4 & 4 & 2 & 3 & 4 & 4 & 2 & 1 & 1 & 999 & 2 & 2 & \#¡NULO! & 62 & 18 & \#¡NULO! & 1 & 1 & \#¡NULO! & 2 & 3 & \#¡NULO! & 3 & 99 & \#¡NULO! & 7 & 88 & 88 & \#¡NULO! & 98 & 98 & \#¡NULO! & 7 & 88 & 88 & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 4 & 4 & 2 & 2 & 2 & 1 & 1 & 4 & 1 & 2 & 1 & 18 & 29 & 7 & 1998 & 11 & 3 & 99 & 9 & 7 & 2 & 2 & 1 & - & 4 & 2 & 88 & 1 & 2 & 0 & 99 & 0 & 99 & 6 & 6 & 3 & 7 & 4 & 1 & 2 & 2 & 2 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & PUENTE ALTO & 2 & 1 & 13 & 1 & 1 & 3.00 & 3.00 & 3.00 & 1.00 \\
2 & 3 & 3 & 3 & 10 & 5 & 10 & 1 & 2 & 2 & 2 & 4 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 5 & \#¡NULO! & 3 & \#¡NULO! & 5 & \#¡NULO! & 2 & 6 & 3 & 6 & 4 & 2 & 5 & 6 & 6 & 2 & 2 & 4 & 4 & 4 & 4 & 4 & 6 & 2 & 6 & 2 & 1 & 2 & 6 & 6 & 4 & 5 & 2 & 3 & 2 & 1 & 2 & 1 & 4 & 1 & 2 & 3 & 3 & 2 & 2 & 3 & 2 & 9 & 2 & 2 & 10 & 2 & 3 & 1 & 3 & 3 & 3 & 3 & 3 & 3 & 2 & 4 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 5 & 10 & 4 & 2 & 4 & 4 & 2 & 3 & 1 & 1 & 1 & 1 & 1 & 2 & 40 & 34 & 35 & 1 & 1 & 1 & 4 & 4 & 4 & 1 & 5 & 3 & 1 & 5 & 1 & 5 & 7 & 2 & 2 & 1 & 1 & 1 & 1 & 999 & 1 & 1 & 1 & \#¡NULO! & 1 & 1 & 1 & \#¡NULO! & 3 & 5 & 3 & \#¡NULO! & 5 & 5 & 5 & 8 & 1 & 4 & 2 & 3 & 3 & 5 & 3 & 1 & 1 & 1 & 1 & 4 & 4 & 5 & 2 & 2 & 2 & 2 & 4 & 2 & 2 & 1 & 57 & 13 & 1 & 1960 & 12 & 4 & 2 & 1 & 9 & 4 & 4 & 1 & - & 3 & 1 & 88 & 1 & 4 & 1 & 4 & 1 & 4 & 99 & 99 & 3 & 7 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 2 & 1 & 1 & 2 & 2 & 1 & 2 & IQUIQUE & 2 & 5 & 1 & 1 & 1 & 2.00 & 1.00 & 3.00 & 2.00 \\
8 & 5 & 1 & 5 & 10 & 10 & 11 & 10 & 7 & 4 & 1 & 4 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 5 & \#¡NULO! & 3 & \#¡NULO! & 3 & \#¡NULO! & 6 & 6 & 5 & 6 & 6 & 6 & 3 & 6 & 6 & 6 & 3 & 2 & 4 & 4 & 4 & 3 & 6 & 6 & 6 & 3 & 2 & 4 & 6 & 6 & 6 & 6 & 1 & 1 & 2 & 1 & 2 & 3 & 4 & 4 & 3 & 2 & 3 & 2 & 3 & 3 & 3 & 1 & 8 & 7 & 1 & 8 & 3 & 2 & 2 & 2 & 2 & 3 & 2 & 2 & 77 & 7 & 7 & 77 & 7 & 7 & 7 & 7 & 7 & 10 & 5 & 3 & 1 & 3 & 3 & 3 & 4 & 1 & 1 & 999 & 2 & 1 & \#¡NULO! & 49 & 50 & \#¡NULO! & 1 & 1 & \#¡NULO! & 1 & 88 & \#¡NULO! & 5 & 5 & \#¡NULO! & 5 & 5 & 5 & \#¡NULO! & 98 & 98 & \#¡NULO! & 1 & 1 & 1 & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 1 & 2 & 4 & 4 & 4 & 1 & 1 & 4 & 2 & 2 & 2 & 2 & 1 & 25 & 8 & 1 & 1992 & 14 & 5 & 1 & 1 & 2 & 5 & 3 & 2 & - & 4 & 1 & 5 & 1 & 1 & 1 & 1 & 0 & 99 & 6 & 6 & 2 & 7 & 3 & 1 & 2 & 2 & 2 & 1 & 1 & 1 & 2 & 2 & 2 & 2 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & PANGUIPULLI & 2 & 2 & 14 & 1 & 1 & 2.00 & 2.00 & 4.00 & 2.00 \\
7 & 2 & 2 & 2 & 8 & 5 & 7 & 12 & 6 & 3 & 1 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 77 & 77 & 1 & \#¡NULO! & 1 & \#¡NULO! & 4 & 6 & 3 & 6 & 2 & 2 & 2 & 6 & 6 & 3 & 2 & 2 & 2 & 6 & 6 & 2 & 6 & 3 & 3 & 2 & 4 & 3 & 2 & 6 & 6 & 2 & 2 & 2 & 2 & 1 & 1 & 1 & 3 & 1 & 3 & 2 & 3 & 3 & 2 & 3 & 3 & 9 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 3 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 1 & 3 & 4 & 1 & 4 & 4 & 1 & 3 & 1 & 1 & 1 & 1 & 2 & 2 & 36 & 42 & 52 & 2 & 1 & 1 & 6 & 6 & 4 & 3 & 3 & 3 & 10 & 10 & 10 & 10 & 7 & 7 & 7 & 10 & 2 & 9 & 8 & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 5 & 5 & 5 & 5 & 5 & 5 & 1 & 5 & 4 & 4 & 4 & 4 & 8 & 8 & 8 & 5 & 8 & 4 & 2 & 2 & 2 & 2 & 1 & 37 & 1 & 10 & 1979 & 20 & 8 & 1 & 1 & 1 & 4 & 99 & 1 & - & 6 & 1 & 88 & 1 & 3 & 0 & 99 & 0 & 99 & 99 & 99 & 3 & 7 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 2 & 2 & SAN JOAQUÍN & 2 & 3 & 13 & 1 & 1 & 2.00 & 3.00 & 4.00 & 1.00 \\
7 & 2 & 2 & 2 & 5 & 5 & 13 & 1 & 11 & 2 & 1 & 2 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 4 & \#¡NULO! & 1 & \#¡NULO! & 3 & \#¡NULO! & 4 & 1 & 1 & 6 & 2 & 2 & 2 & 6 & 6 & 2 & 3 & 1 & 2 & 4 & 4 & 4 & 6 & 1 & 4 & 2 & 5 & 1 & 1 & 4 & 4 & 3 & 1 & 2 & 2 & 1 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 3 & 10 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 3 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 1 & 2 & 4 & 1 & 2 & 4 & 4 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 61 & 58 & 54 & 1 & 1 & 1 & 4 & 4 & 2 & 5 & 5 & 5 & 10 & 10 & 10 & 10 & 7 & 7 & 7 & 1 & 1 & 1 & 1 & 1 & 999 & 999 & 1 & 4 & \#¡NULO! & \#¡NULO! & 1 & 3 & \#¡NULO! & \#¡NULO! & 4 & 5 & \#¡NULO! & \#¡NULO! & 7 & 4 & 4 & 4 & 4 & 2 & 4 & 2 & 4 & 4 & 4 & 4 & 4 & 2 & 2 & 4 & 2 & 2 & 4 & 2 & 2 & 2 & 2 & 1 & 50 & 10 & 12 & 1966 & 12 & 4 & 1 & 2 & 1 & 4 & 3 & 1 & - & 2 & 1 & 88 & 1 & 2 & 0 & 99 & 0 & 99 & 6 & 7 & 3 & 5 & 3 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & 2 & FUTRONO & 2 & 4 & 14 & 1 & 1 & 2.00 & 3.00 & 3.00 & 2.00 \\
7 & 2 & 2 & 2 & 9 & 5 & 11 & 1 & 5 & 2 & 1 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 4 & \#¡NULO! & 1 & \#¡NULO! & 1 & \#¡NULO! & 4 & 6 & 3 & 6 & 1 & 6 & 1 & 2 & 6 & 2 & 1 & 1 & 8 & 8 & 3 & 1 & 6 & 1 & 3 & 3 & 5 & 1 & 6 & 5 & 2 & 1 & 1 & 2 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 3 & 1 & 1 & 1 & 1 & 10 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 2 & 3 & 1 & 3 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 10 & 7 & 4 & 1 & 1 & 3 & 3 & 3 & 1 & 1 & 1 & 2 & 1 & 1 & 27 & 35 & 70 & 1 & 1 & 9 & 4 & 4 & 88 & 5 & 5 & 5 & 10 & 10 & 10 & 10 & 7 & 7 & 7 & 1 & 1 & 1 & 1 & 999 & 999 & 1 & 1 & \#¡NULO! & \#¡NULO! & 1 & 2 & \#¡NULO! & \#¡NULO! & 3 & 3 & \#¡NULO! & \#¡NULO! & 5 & 5 & 8 & 4 & 2 & 2 & 2 & 4 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & 2 & 2 & 2 & 2 & 4 & 2 & 2 & 2 & 2 & 1 & 60 & 10 & 1 & 1957 & 8 & 2 & 2 & 1 & 9 & 2 & 1 & 1 & - & 5 & 1 & 88 & 1 & 2 & 0 & 99 & 0 & 99 & 5 & 88 & 3 & 4 & 3 & 1 & 1 & 1 & 2 & 2 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & SAN IGNACIO & 2 & 5 & 8 & 0 & 2 & 2.00 & 3.00 & 2.00 & 2.00 \\
4 & 1 & 2 & 2 & 9 & 5 & 16 & 3 & 1 & 4 & 2 & 3 & 3 & 2 & 1 & 2 & 1 & 1 & 1 & 3 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 1 & 6 & 5 & 6 & 3 & 4 & 4 & 4 & 3 & 4 & 3 & 5 & 3 & 1 & 1 & 4 & 3 & 3 & 4 & 3 & 1 & 3 & 3 & 1 & 3 & 4 & 2 & 1 & 2 & 1 & 2 & 3 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 3 & 10 & 4 & 4 & 10 & 4 & 3 & 2 & 2 & 1 & 3 & 3 & 3 & 2 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 2 & 3 & 3 & 1 & 5 & 3 & 1 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 33 & 74 & 33 & 1 & 1 & 1 & 8 & 4 & 8 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 4 & 4 & 4 & 1 & 1 & 1 & 1 & 999 & 999 & 1 & 1 & \#¡NULO! & \#¡NULO! & 1 & 2 & \#¡NULO! & \#¡NULO! & 3 & 3 & \#¡NULO! & \#¡NULO! & 88 & 5 & 8 & 8 & 8 & 2 & 8 & 8 & 5 & 8 & 1 & 3 & 1 & 4 & 2 & 4 & 2 & 2 & 2 & 1 & 2 & 2 & 3 & 2 & 1 & 66 & 9 & 3 & 1951 & 12 & 4 & 2 & 1 & 8 & 4 & 4 & 1 & - & 2 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 6 & 6 & 3 & 7 & 3 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & TEMUCO & 2 & 5 & 9 & 1 & 1 & 2.00 & 1.00 & 3.00 & 2.00 \\
8 & 1 & 1 & 1 & 6 & 8 & 2 & 8 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & 2 & 1 & 1 & 1 & 9 & \#¡NULO! & 5 & 5 & 5 & \#¡NULO! & 2 & 6 & 3 & 6 & 3 & 3 & 2 & 6 & 6 & 3 & 2 & 3 & 4 & 2 & 2 & 1 & 6 & 6 & 3 & 2 & 3 & 4 & 3 & 1 & 3 & 4 & 2 & 2 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 1 & 2 & 1 & 2 & 3 & 10 & 8 & 7 & 9 & 8 & 3 & 3 & 3 & 3 & 3 & 3 & 2 & 1 & 8 & 7 & 8 & 8 & 7 & 8 & 8 & 7 & 8 & 2 & 10 & 3 & 1 & 2 & 3 & 3 & 2 & 1 & 1 & 999 & 2 & 1 & \#¡NULO! & 18 & 18 & \#¡NULO! & 3 & 2 & \#¡NULO! & 5 & 6 & \#¡NULO! & 4 & 5 & \#¡NULO! & 4 & 4 & 4 & \#¡NULO! & 8 & 8 & \#¡NULO! & 10 & 6 & 10 & \#¡NULO! & 1 & 999 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 4 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 5 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 3 & 4 & 3 & 2 & 4 & 8 & 5 & 1 & 2 & 2 & 2 & 4 & 4 & 4 & 1 & 2 & 1 & 1 & 2 & 1 & 2 & 2 & 1 & 19 & 27 & 8 & 1997 & 12 & 4 & 2 & 1 & 7 & 4 & 3 & 10 & - & 8 & 1 & 5 & 1 & 2 & 1 & 2 & 1 & 1 & 9 & 9 & 2 & 7 & 3 & 1 & 1 & 2 & 2 & 1 & 1 & 1 & 2 & 2 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & PEDRO AGUIRRE CERDA & 2 & 1 & 13 & 1 & 1 & 2.00 & 1.00 & 3.00 & 1.00 \\
4 & 1 & 1 & 1 & 6 & 7 & 10 & 1 & 7 & 3 & 1 & 3 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 6 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 2 & 2 & 4 & 6 & 3 & 3 & 4 & 4 & 6 & 4 & 4 & 4 & 2 & 4 & 2 & 3 & 6 & 3 & 4 & 3 & 2 & 3 & 2 & 2 & 4 & 2 & 2 & 2 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 3 & 2 & 10 & 4 & 7 & 10 & 4 & 3 & 3 & 3 & 1 & 3 & 3 & 3 & 3 & 4 & 4 & 4 & 3 & 4 & 88 & 4 & 4 & 3 & 5 & 4 & 1 & 1 & 4 & 3 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 33 & 30 & 35 & 8 & 8 & 2 & 9 & 9 & 8 & 4 & 4 & 3 & 2 & 3 & 5 & 5 & 2 & 3 & 4 & 10 & 10 & 10 & 88 & 1 & 1 & 1 & 1 & 2 & 3 & 1 & 2 & 4 & 1 & 1 & 5 & 5 & 4 & 3 & 8 & 4 & 2 & 2 & 1 & 4 & 4 & 4 & 2 & 1 & 1 & 1 & 1 & 3 & 4 & 4 & 1 & 1 & 4 & 1 & 2 & 1 & 2 & 1 & 34 & 30 & 8 & 1982 & 20 & 9 & 1 & 1 & 1 & 9 & 6 & 9 & - & 8 & 1 & 88 & 1 & 1 & 1 & 1 & 1 & 1 & 12 & 12 & 2 & 7 & 1 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 2 & 1 & 1 & 2 & 1 & 1 & 2 & 1 & 1 & 2 & LINARES & 2 & 2 & 7 & 1 & 1 & 1.00 & 1.00 & 4.00 & 2.00 \\
7 & 2 & 2 & 2 & 10 & 10 & 12 & 11 & 7 & 3 & 2 & 4 & 3 & 1 & 2 & 2 & 2 & 2 & 2 & 77 & 77 & 5 & 5 & 1 & \#¡NULO! & 5 & 2 & 2 & 2 & 2 & 1 & 1 & 1 & 2 & 2 & 3 & 1 & 2 & 2 & 1 & 2 & 2 & 1 & 2 & 5 & 5 & 2 & 3 & 1 & 2 & 2 & 1 & 3 & 3 & 1 & 2 & 1 & 1 & 1 & 2 & 2 & 3 & 2 & 3 & 3 & 3 & 10 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 3 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 1 & 2 & 3 & 1 & 3 & 3 & 3 & 1 & 1 & 1 & 999 & 2 & 2 & \#¡NULO! & 71 & 40 & \#¡NULO! & 1 & 1 & \#¡NULO! & 8 & 8 & \#¡NULO! & 1 & 1 & \#¡NULO! & 10 & 10 & 10 & \#¡NULO! & 7 & 7 & \#¡NULO! & 10 & 10 & 10 & \#¡NULO! & 1 & 999 & 999 & 999 & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 10 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 3 & 4 & 4 & 4 & 4 & 3 & 3 & 5 & 4 & 3 & 3 & 2 & 2 & 2 & 2 & 1 & 39 & 99 & 99 & 9999 & 17 & 8 & 1 & 1 & 1 & 8 & 5 & 1 & - & 8 & 1 & 88 & 1 & 3 & 0 & 99 & 0 & 99 & 14 & 14 & 3 & 7 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & VITACURA & 2 & 3 & 13 & 1 & 1 & 1.00 & 3.00 & 4.00 & 1.00 \\
4 & 1 & 1 & 1 & 5 & 6 & 11 & 1 & 10 & 2 & 2 & 4 & 3 & 2 & 3 & 2 & 2 & 1 & 1 & 2 & \#¡NULO! & 3 & \#¡NULO! & 3 & \#¡NULO! & 4 & 6 & 4 & 3 & 2 & 2 & 2 & 4 & 3 & 4 & 3 & 5 & 2 & 2 & 2 & 4 & 1 & 2 & 4 & 4 & 2 & 4 & 2 & 1 & 2 & 4 & 2 & 3 & 3 & 1 & 2 & 3 & 3 & 1 & 2 & 1 & 3 & 2 & 3 & 3 & 3 & 10 & 4 & 7 & 10 & 4 & 8 & 3 & 2 & 1 & 3 & 3 & 3 & 2 & 4 & 4 & 4 & 4 & 7 & 4 & 4 & 7 & 4 & 4 & 7 & 3 & 1 & 3 & 3 & 2 & 4 & 1 & 1 & 999 & 1 & 1 & \#¡NULO! & 55 & 48 & \#¡NULO! & 1 & 1 & \#¡NULO! & 8 & 8 & \#¡NULO! & 3 & 3 & \#¡NULO! & 5 & 7 & 7 & \#¡NULO! & 7 & 7 & \#¡NULO! & 8 & 8 & 8 & \#¡NULO! & 1 & 999 & 1 & 1 & 2 & \#¡NULO! & 1 & 1 & 3 & \#¡NULO! & 3 & 2 & 9 & \#¡NULO! & 5 & 7 & 3 & 3 & 3 & 2 & 3 & 3 & 3 & 2 & 3 & 3 & 3 & 4 & 2 & 2 & 4 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 1 & 76 & 99 & 99 & 9999 & 14 & 6 & 3 & 9 & 8 & 6 & 4 & 1 & - & 5 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 99 & 99 & 3 & 4 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & MOLINA & 2 & 5 & 7 & 0 & 1 & 2.00 & 2.00 & 4.00 & 2.00 \\
7 & 2 & 2 & 2 & 10 & 5 & 10 & 14 & 7 & 4 & 2 & 4 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & \#¡NULO! & 1 & \#¡NULO! & 1 & \#¡NULO! & 2 & 2 & 3 & 2 & 2 & 2 & 2 & 2 & 6 & 2 & 2 & 2 & 2 & 2 & 2 & 4 & 6 & 2 & 2 & 2 & 5 & 4 & 2 & 2 & 2 & 2 & 1 & 2 & 3 & 1 & 2 & 2 & 1 & 1 & 1 & 1 & 3 & 2 & 2 & 3 & 3 & 10 & 7 & 7 & 10 & 7 & 2 & 2 & 2 & 2 & 2 & 2 & 1 & 2 & 7 & 7 & 7 & 8 & 8 & 8 & 8 & 8 & 8 & 5 & 6 & 4 & 2 & 1 & 1 & 1 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 46 & 45 & 90 & 1 & 1 & 1 & 2 & 6 & 2 & 1 & 3 & 1 & 10 & 10 & 5 & 10 & 98 & 98 & 98 & 1 & 88 & 88 & 88 & 999 & 999 & 1 & 1 & \#¡NULO! & \#¡NULO! & 4 & 1 & \#¡NULO! & \#¡NULO! & 3 & 3 & \#¡NULO! & \#¡NULO! & 6 & 6 & 5 & 5 & 5 & 5 & 5 & 5 & 1 & 3 & 1 & 1 & 1 & 1 & 2 & 4 & 2 & 2 & 2 & 4 & 2 & 2 & 2 & 2 & 1 & 49 & 29 & 7 & 1967 & 12 & 4 & 2 & 99 & 9 & 4 & 1 & 8 & solo cree en dios & 8 & 1 & 88 & 1 & 1 & 1 & 2 & 0 & 99 & 7 & 7 & 3 & 6 & 3 & 1 & 2 & 1 & 2 & 1 & 2 & 1 & 2 & 2 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & CHIMBARONGO & 2 & 4 & 6 & 1 & 1 & 2.00 & 3.00 & 3.00 & 2.00 \\
8 & 1 & 1 & 1 & 8 & 5 & 1 & 5 & 12 & 4 & 2 & 4 & 1 & 1 & 1 & 1 & 1 & 1 & 8 & 2 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 6 & 6 & 4 & 6 & 6 & 4 & 6 & 6 & 6 & 6 & 4 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 3 & 4 & 6 & 6 & 6 & 4 & 2 & 3 & 1 & 1 & 1 & 1 & 3 & 3 & 2 & 2 & 1 & 2 & 2 & 3 & 3 & 0 & 8 & 7 & 0 & 8 & 2 & 3 & 2 & 3 & 3 & 3 & 3 & 1 & 8 & 7 & 7 & 7 & 7 & 8 & 8 & 8 & 8 & 7 & 10 & 2 & 2 & 2 & 1 & 3 & 3 & 1 & 1 & 999 & 1 & 2 & \#¡NULO! & 38 & 36 & \#¡NULO! & 4 & 4 & \#¡NULO! & 6 & 6 & \#¡NULO! & 3 & 3 & \#¡NULO! & 7 & 8 & 3 & \#¡NULO! & 7 & 8 & \#¡NULO! & 4 & 1 & 1 & \#¡NULO! & 999 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 8 & 8 & 2 & 8 & 8 & 8 & 3 & 2 & 1 & 1 & 1 & 1 & 4 & 4 & 2 & 1 & 2 & 4 & 1 & 2 & 1 & 2 & 1 & 32 & 1 & 11 & 1984 & 20 & 9 & 1 & 1 & 1 & 9 & 5 & 2 & - & 2 & 2 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 11 & 11 & 2 & 7 & 3 & 1 & 2 & 2 & 2 & 1 & 2 & 1 & 2 & 2 & 2 & 1 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & MAIPÚ & 2 & 2 & 13 & 1 & 1 & 2.00 & 3.00 & 4.00 & 1.00 \\
11 & 5 & 1 & 5 & 9 & 6 & 1 & 3 & 11 & 3 & 1 & 4 & 2 & 2 & 2 & 2 & 1 & 1 & 1 & 77 & 77 & 5 & 5 & 7 & 7 & 2 & 4 & 3 & 6 & 2 & 2 & 2 & 3 & 6 & 4 & 2 & 3 & 4 & 3 & 3 & 3 & 2 & 4 & 6 & 4 & 2 & 4 & 3 & 6 & 3 & 2 & 2 & 2 & 2 & 2 & 1 & 4 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 0 & 99 & 99 & 0 & 8 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 2 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 3 & 10 & 5 & 2 & 8 & 8 & 8 & 4 & 1 & 1 & 999 & 1 & 2 & \#¡NULO! & 49 & 50 & \#¡NULO! & 4 & 4 & \#¡NULO! & 8 & 8 & \#¡NULO! & 3 & 4 & \#¡NULO! & 88 & 8 & 4 & \#¡NULO! & 99 & 99 & \#¡NULO! & 7 & 88 & 10 & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 3 & 3 & 4 & 4 & 4 & 2 & 3 & 2 & 1 & 3 & 2 & 2 & 2 & 1 & 44 & 14 & 11 & 1972 & 16 & 6 & 1 & 1 & 1 & 6 & 4 & 1 & - & 7 & 1 & 88 & 1 & 2 & 0 & 99 & 0 & 99 & 11 & 11 & 3 & 7 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 2 & 1 & 1 & 2 & 2 & 1 & 2 & PUENTE ALTO & 2 & 3 & 13 & 1 & 1 & 2.00 & 9.00 & 4.00 & 1.00 \\
7 & 2 & 2 & 2 & 8 & 6 & 3 & 9 & 14 & 2 & 1 & 4 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 77 & 77 & 1 & \#¡NULO! & 3 & \#¡NULO! & 3 & 1 & 1 & 4 & 2 & 1 & 1 & 1 & 1 & 3 & 3 & 2 & 2 & 4 & 4 & 4 & 2 & 1 & 3 & 2 & 5 & 2 & 1 & 2 & 4 & 4 & 1 & 2 & 2 & 1 & 2 & 3 & 2 & 1 & 1 & 1 & 3 & 1 & 1 & 3 & 3 & 10 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 2 & 3 & 1 & 3 & 5 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 1 & 3 & 3 & 1 & 2 & 4 & 4 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 60 & 63 & 62 & 1 & 1 & 8 & 8 & 8 & 6 & 3 & 3 & 3 & 6 & 5 & 8 & 4 & 7 & 7 & 4 & 1 & 4 & 1 & 4 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 2 & 3 & 4 & 5 & 2 & 6 & 6 & 7 & 3 & 5 & 4 & 3 & 4 & 2 & 5 & 1 & 5 & 1 & 2 & 2 & 3 & 2 & 4 & 3 & 3 & 2 & 3 & 2 & 3 & 2 & 2 & 1 & 61 & 29 & 8 & 1955 & 16 & 8 & 1 & 3 & 1 & 8 & 4 & 1 & - & 8 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 11 & 11 & 3 & 7 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & VALDIVIA & 2 & 5 & 14 & 1 & 1 & 2.00 & 2.00 & 4.00 & 2.00 \\
9 & 1 & 3 & 3 & 6 & 7 & 2 & 3 & 9 & 3 & 2 & 2 & 2 & 2 & 1 & 1 & 1 & 1 & 1 & 5 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 4 & 6 & 5 & 6 & 2 & 6 & 2 & 6 & 6 & 3 & 3 & 4 & 6 & 6 & 6 & 4 & 6 & 6 & 6 & 3 & 3 & 3 & 6 & 6 & 3 & 2 & 3 & 3 & 3 & 1 & 2 & 4 & 4 & 2 & 2 & 3 & 3 & 2 & 2 & 3 & 3 & 5 & 99 & 7 & 5 & 88 & 3 & 3 & 3 & 2 & 3 & 3 & 2 & 3 & 4 & 7 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 3 & 7 & 5 & 1 & 2 & 2 & 2 & 4 & 1 & 1 & 1 & 1 & 2 & 2 & 38 & 65 & 35 & 1 & 1 & 8 & 4 & 2 & 4 & 5 & 5 & 3 & 3 & 4 & 4 & 3 & 4 & 4 & 4 & 3 & 2 & 1 & 3 & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 4 & 3 & 2 & 8 & 8 & 3 & 3 & 2 & 2 & 2 & 3 & 2 & 2 & 1 & 2 & 2 & 1 & 2 & 4 & 4 & 2 & 1 & 40 & 10 & 11 & 1976 & 14 & 6 & 2 & 1 & 5 & 6 & 3 & 1 & - & 5 & 1 & 88 & 1 & 1 & 1 & 1 & 0 & 99 & 99 & 99 & 3 & 6 & 4 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 2 & 1 & 2 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & 2 & MOLINA & 2 & 3 & 7 & 1 & 1 & 3.00 & 1.00 & 4.00 & 2.00 \\
7 & 2 & 2 & 2 & 7 & 4 & 1 & 6 & 11 & 2 & 3 & 2 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 4 & \#¡NULO! & 5 & 5 & 6 & 6 & 2 & 6 & 1 & 6 & 6 & 6 & 2 & 6 & 6 & 6 & 6 & 2 & 6 & 3 & 3 & 2 & 6 & 2 & 6 & 6 & 2 & 6 & 6 & 6 & 2 & 2 & 3 & 3 & 3 & 1 & 1 & 4 & 4 & 2 & 3 & 3 & 3 & 1 & 1 & 3 & 2 & 1 & 2 & 2 & 5 & 2 & 3 & 1 & 3 & 3 & 3 & 3 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 7 & 5 & 5 & 1 & 3 & 3 & 3 & 4 & 1 & 1 & 1 & 2 & 1 & 2 & 17 & 34 & 38 & 1 & 1 & 1 & 4 & 4 & 4 & 2 & 4 & 4 & 5 & 5 & 5 & 5 & 2 & 2 & 2 & 8 & 8 & 8 & 8 & 999 & 999 & 1 & 1 & \#¡NULO! & \#¡NULO! & 1 & 1 & \#¡NULO! & \#¡NULO! & 1 & 1 & \#¡NULO! & \#¡NULO! & 5 & 5 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 4 & 4 & 1 & 1 & 1 & 1 & 2 & 4 & 4 & 2 & 1 & 63 & 30 & 8 & 1953 & 12 & 4 & 1 & 2 & 1 & 4 & 3 & 1 & - & 5 & 2 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 5 & 5 & 3 & 6 & 4 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & COIHAIQUE & 2 & 5 & 11 & 2 & 1 & 3.00 & 2.00 & 3.00 & 2.00 \\
7 & 2 & 2 & 2 & 10 & 5 & 3 & 5 & 11 & 4 & 2 & 1 & 2 & 2 & 8 & 8 & 1 & 1 & 1 & 77 & 77 & 5 & 5 & 7 & 7 & 6 & 6 & 4 & 6 & 6 & 6 & 4 & 6 & 6 & 6 & 6 & 8 & 6 & 6 & 6 & 8 & 6 & 8 & 6 & 6 & 5 & 6 & 6 & 6 & 6 & 6 & 8 & 8 & 8 & 2 & 1 & 4 & 4 & 4 & 3 & 3 & 3 & 2 & 3 & 3 & 3 & 0 & 7 & 7 & 0 & 7 & 3 & 2 & 3 & 3 & 3 & 3 & 1 & 3 & 77 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 8 & 5 & 2 & 1 & 8 & 8 & 8 & 4 & 1 & 1 & 999 & 1 & 2 & \#¡NULO! & 19 & 42 & \#¡NULO! & 3 & 1 & \#¡NULO! & 7 & 4 & \#¡NULO! & 2 & 2 & \#¡NULO! & 99 & 88 & 1 & \#¡NULO! & 98 & 88 & \#¡NULO! & 9 & 9 & 9 & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 1 & 1 & 1 & 3 & 3 & 4 & 2 & 2 & 2 & 3 & 2 & 4 & 3 & 2 & 1 & 22 & 6 & 7 & 1994 & 12 & 4 & 3 & 9 & 7 & 4 & 3 & 2 & - & 2 & 2 & 88 & 1 & 2 & 1 & 4 & 1 & 1 & 99 & 9 & 3 & 7 & 3 & 1 & 2 & 2 & 1 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & CHILLÁN & 2 & 1 & 8 & 1 & 1 & 2.00 & 9.00 & 3.00 & 2.00 \\
7 & 2 & 2 & 2 & 10 & 5 & 1 & 6 & 3 & 3 & 2 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 2 & 1 & \#¡NULO! & 1 & \#¡NULO! & 1 & \#¡NULO! & 3 & 6 & 1 & 2 & 2 & 2 & 1 & 2 & 6 & 2 & 2 & 2 & 1 & 2 & 3 & 1 & 1 & 2 & 2 & 3 & 5 & 1 & 2 & 4 & 3 & 1 & 1 & 2 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 2 & 2 & 10 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 3 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 1 & 5 & 3 & 1 & 1 & 5 & 5 & 2 & 1 & 1 & 1 & 2 & 1 & 2 & 52 & 50 & 55 & 8 & 8 & 8 & 4 & 4 & 4 & 3 & 3 & 3 & 10 & 10 & 10 & 10 & 7 & 7 & 8 & 1 & 1 & 1 & 9 & 999 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 10 & 5 & 5 & 5 & 5 & 5 & 5 & 1 & 5 & 4 & 4 & 4 & 4 & 3 & 4 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 68 & 25 & 11 & 1948 & 12 & 4 & 2 & 1 & 8 & 4 & 99 & 1 & - & 2 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 8 & 8 & 3 & 7 & 3 & 1 & 2 & 2 & 1 & 1 & 2 & 1 & 2 & 2 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & LINARES & 2 & 5 & 7 & 0 & 1 & 2.00 & 3.00 & 3.00 & 2.00 \\
9 & 3 & 3 & 3 & 2 & 88 & 6 & 5 & 1 & 3 & 2 & 3 & 3 & 3 & 3 & 2 & 2 & 2 & 2 & 77 & 77 & 8 & 5 & 7 & 7 & 8 & 3 & 2 & 6 & 6 & 6 & 3 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 6 & 3 & 6 & 6 & 6 & 6 & 3 & 3 & 6 & 6 & 3 & 6 & 8 & 8 & 8 & 2 & 1 & 4 & 4 & 4 & 3 & 3 & 3 & 2 & 2 & 3 & 3 & 1 & 99 & 7 & 1 & 77 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 10 & 2 & 4 & 8 & 8 & 8 & 8 & 4 & 1 & 1 & 999 & 2 & 2 & \#¡NULO! & 32 & 40 & \#¡NULO! & 8 & 1 & \#¡NULO! & 88 & 1 & \#¡NULO! & 2 & 3 & \#¡NULO! & 88 & 88 & 88 & \#¡NULO! & 98 & 88 & \#¡NULO! & 8 & 88 & 88 & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 2 & 2 & 2 & 2 & 2 & 4 & 4 & 2 & 2 & 5 & 5 & 3 & 2 & 2 & 1 & 31 & 24 & 2 & 1986 & 8 & 2 & 2 & 1 & 5 & 2 & 1 & 9 & - & 8 & 2 & 88 & 1 & 1 & 1 & 10 & 0 & 99 & 99 & 99 & 3 & 7 & 4 & 1 & 2 & 2 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & RANCAGUA & 2 & 2 & 6 & 1 & 1 & 3.00 & 9.00 & 2.00 & 2.00 \\
2 & 1 & 1 & 1 & 10 & 5 & 1 & 13 & 10 & 3 & 3 & 3 & 4 & 2 & 2 & 2 & 2 & 2 & 2 & 6 & \#¡NULO! & 5 & 8 & 4 & \#¡NULO! & 4 & 6 & 4 & 3 & 6 & 6 & 4 & 6 & 6 & 4 & 3 & 2 & 6 & 6 & 8 & 2 & 6 & 6 & 6 & 6 & 2 & 4 & 6 & 6 & 3 & 3 & 3 & 2 & 1 & 1 & 2 & 2 & 2 & 1 & 1 & 1 & 3 & 1 & 1 & 1 & 3 & 10 & 8 & 7 & 10 & 8 & 3 & 2 & 3 & 3 & 3 & 3 & 3 & 1 & 8 & 7 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 2 & 4 & 3 & 1 & 8 & 8 & 8 & 3 & 1 & 999 & 999 & 2 & \#¡NULO! & \#¡NULO! & 66 & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & 88 & 88 & \#¡NULO! & \#¡NULO! & 7 & \#¡NULO! & \#¡NULO! & 4 & 6 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 6 & 8 & 2 & 8 & 8 & 8 & 8 & 5 & 2 & 2 & 2 & 3 & 4 & 4 & 4 & 4 & 4 & 3 & 3 & 2 & 4 & 3 & 2 & 1 & 72 & 6 & 4 & 1945 & 3 & 1 & 2 & 1 & 8 & 1 & 3 & 2 & - & 2 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 5 & 5 & 3 & 4 & 4 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & ALGARROBO & 2 & 5 & 5 & 1 & 1 & 3.00 & 9.00 & 1.00 & 2.00 \\
11 & 1 & 5 & 1 & 10 & 5 & 1 & 3 & 5 & 4 & 2 & 4 & 3 & 2 & 1 & 2 & 1 & 1 & 1 & 3 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 6 & 6 & 4 & 6 & 3 & 3 & 2 & 4 & 2 & 4 & 4 & 3 & 3 & 6 & 2 & 4 & 6 & 2 & 6 & 2 & 2 & 2 & 2 & 2 & 3 & 2 & 3 & 8 & 8 & 1 & 2 & 4 & 3 & 1 & 3 & 2 & 3 & 2 & 3 & 3 & 3 & 6 & 21 & 7 & 10 & 77 & 3 & 3 & 3 & 2 & 3 & 3 & 3 & 3 & 77 & 7 & 7 & 88 & 88 & 88 & 88 & 88 & 88 & 1 & 8 & 3 & 1 & 3 & 4 & 3 & 4 & 1 & 999 & 999 & 2 & \#¡NULO! & \#¡NULO! & 44 & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & 8 & \#¡NULO! & \#¡NULO! & 5 & \#¡NULO! & \#¡NULO! & 4 & 4 & \#¡NULO! & \#¡NULO! & 98 & \#¡NULO! & \#¡NULO! & 10 & 10 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 4 & 1 & 1 & 3 & 4 & 4 & 4 & 2 & 4 & 4 & 2 & 2 & 2 & 2 & 1 & 66 & 7 & 9 & 1950 & 12 & 4 & 2 & 1 & 8 & 4 & 4 & 1 & - & 4 & 1 & 88 & 1 & 2 & 0 & 99 & 0 & 99 & 10 & 11 & 3 & 4 & 3 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 2 & 2 & VALDIVIA & 2 & 5 & 14 & 1 & 1 & 2.00 & 1.00 & 3.00 & 2.00 \\
7 & 2 & 2 & 2 & 10 & 1 & 6 & 11 & 14 & 2 & 2 & 4 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 1 & \#¡NULO! & 1 & \#¡NULO! & 2 & \#¡NULO! & 3 & 2 & 2 & 3 & 6 & 2 & 4 & 3 & 2 & 3 & 3 & 2 & 2 & 3 & 3 & 2 & 3 & 3 & 2 & 2 & 4 & 3 & 3 & 3 & 3 & 3 & 1 & 2 & 2 & 1 & 2 & 1 & 2 & 1 & 2 & 3 & 3 & 3 & 2 & 1 & 3 & 10 & 7 & 7 & 10 & 7 & 3 & 3 & 3 & 3 & 3 & 3 & 1 & 3 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 7 & 1 & 2 & 4 & 1 & 2 & 4 & 4 & 3 & 1 & 999 & 999 & 2 & \#¡NULO! & \#¡NULO! & 43 & \#¡NULO! & \#¡NULO! & 8 & \#¡NULO! & \#¡NULO! & 4 & \#¡NULO! & \#¡NULO! & 4 & \#¡NULO! & \#¡NULO! & 10 & 88 & \#¡NULO! & \#¡NULO! & 7 & \#¡NULO! & \#¡NULO! & 10 & 10 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 3 & 2 & 4 & 4 & 4 & 4 & 2 & 4 & 4 & 2 & 2 & 2 & 2 & 4 & 2 & 4 & 4 & 2 & 2 & 4 & 4 & 2 & 1 & 37 & 23 & 11 & 1979 & 17 & 8 & 1 & 2 & 1 & 8 & 88 & 8 & luterana & 2 & 1 & 88 & 1 & 2 & 0 & 99 & 0 & 99 & 12 & 12 & 1 & 7 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & OSORNO & 2 & 3 & 10 & 1 & 1 & 1.00 & 3.00 & 4.00 & 2.00 \\
9 & 3 & 3 & 3 & 4 & 6 & 6 & 11 & 1 & 1 & 3 & 3 & 4 & 3 & 2 & 2 & 2 & 2 & 2 & 77 & 77 & 5 & 5 & 7 & 7 & 3 & 6 & 3 & 6 & 4 & 6 & 3 & 6 & 6 & 3 & 4 & 4 & 2 & 3 & 3 & 4 & 6 & 6 & 4 & 3 & 3 & 3 & 6 & 2 & 4 & 3 & 3 & 3 & 3 & 2 & 1 & 4 & 4 & 1 & 2 & 3 & 3 & 2 & 2 & 3 & 3 & 0 & 99 & 99 & 0 & 77 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 8 & 7 & 7 & 77 & 7 & 4 & 8 & 7 & 77 & 2 & 8 & 3 & 1 & 8 & 8 & 8 & 4 & 1 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & 50 & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & 99 & 88 & \#¡NULO! & \#¡NULO! & 4 & \#¡NULO! & \#¡NULO! & 2 & 1 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 2 & 2 & 2 & 4 & 8 & 3 & 2 & 2 & 2 & 2 & 2 & 8 & 2 & 4 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & 1 & 24 & 15 & 11 & 1992 & 12 & 4 & 2 & 1 & 5 & 1 & 2 & 3 & - & 4 & 2 & 88 & 1 & 4 & 1 & 1 & 1 & 2 & 2 & 7 & 2 & 6 & 4 & 1 & 2 & 1 & 2 & 1 & 2 & 1 & 2 & 2 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & 2 & 2 & 2 & SAN JAVIER & 2 & 1 & 7 & 0 & 2 & 3.00 & 9.00 & 3.00 & 2.00 \\
4 & 1 & 1 & 1 & 8 & 6 & 3 & 7 & 10 & 2 & 2 & 3 & 3 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & \#¡NULO! & 3 & \#¡NULO! & 4 & \#¡NULO! & 2 & 6 & 5 & 6 & 4 & 3 & 2 & 3 & 6 & 4 & 3 & 4 & 4 & 2 & 2 & 4 & 6 & 4 & 3 & 2 & 1 & 4 & 4 & 1 & 3 & 2 & 2 & 1 & 1 & 1 & 2 & 2 & 2 & 1 & 3 & 3 & 3 & 2 & 2 & 2 & 3 & 10 & 4 & 4 & 10 & 4 & 3 & 3 & 2 & 1 & 3 & 2 & 3 & 2 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 4 & 1 & 3 & 3 & 1 & 3 & 3 & 3 & 4 & 1 & 999 & 999 & 2 & \#¡NULO! & \#¡NULO! & 33 & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & 8 & \#¡NULO! & \#¡NULO! & 4 & \#¡NULO! & \#¡NULO! & 5 & 5 & \#¡NULO! & \#¡NULO! & 7 & \#¡NULO! & \#¡NULO! & 1 & 1 & \#¡NULO! & \#¡NULO! & 999 & 1 & 999 & 1 & \#¡NULO! & 2 & \#¡NULO! & 2 & \#¡NULO! & 2 & \#¡NULO! & 2 & \#¡NULO! & 88 & \#¡NULO! & 88 & 9 & 3 & 3 & 2 & 4 & 2 & 4 & 2 & 2 & 2 & 2 & 2 & 2 & 3 & 3 & 3 & 3 & 3 & 3 & 3 & 2 & 2 & 1 & 63 & 14 & 2 & 1954 & 17 & 8 & 1 & 2 & 3 & 8 & 2 & 1 & - & 5 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 99 & 99 & 3 & 4 & 3 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & 9 & LAS CABRAS & 2 & 5 & 6 & 0 & 2 & 2.00 & 2.00 & 4.00 & 2.00 \\
4 & 1 & 3 & 3 & 9 & 3 & 1 & 5 & 10 & 3 & 2 & 4 & 2 & 1 & 1 & 2 & 2 & 1 & 1 & 5 & \#¡NULO! & 8 & 8 & 4 & \#¡NULO! & 2 & 1 & 5 & 6 & 4 & 6 & 2 & 6 & 6 & 3 & 2 & 4 & 4 & 2 & 6 & 3 & 6 & 3 & 6 & 6 & 3 & 3 & 3 & 2 & 3 & 4 & 8 & 8 & 8 & 1 & 2 & 3 & 3 & 1 & 1 & 1 & 3 & 1 & 3 & 3 & 3 & 10 & 99 & 7 & 10 & 4 & 3 & 3 & 3 & 2 & 3 & 3 & 3 & 3 & 4 & 7 & 77 & 7 & 4 & 4 & 4 & 4 & 4 & 10 & 5 & 1 & 1 & 8 & 8 & 8 & 3 & 1 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & 24 & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & 7 & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & 2 & 3 & \#¡NULO! & \#¡NULO! & 98 & \#¡NULO! & \#¡NULO! & 1 & 88 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & \#¡NULO! & 5 & 5 & 3 & 4 & 2 & 4 & 3 & 3 & 3 & 1 & 1 & 1 & 1 & 4 & 4 & 3 & 3 & 3 & 4 & 2 & 2 & 2 & 2 & 1 & 44 & 11 & 11 & 1972 & 17 & 8 & 1 & 1 & 1 & 8 & 4 & 9 & - & 2 & 1 & 88 & 1 & 1 & 0 & 99 & 0 & 99 & 88 & 88 & 3 & 7 & 3 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 2 & 1 & 1 & 2 & 1 & 1 & 2 & 2 & 2 & 2 & CAÑETE & 2 & 3 & 8 & 1 & 1 & 2.00 & 1.00 & 4.00 & 2.00 \\
9 & 3 & 3 & 3 & 10 & 1 & 2 & 3 & 7 & 1 & 2 & 2 & 3 & 3 & 2 & 2 & 2 & 2 & 2 & 77 & 77 & 5 & 5 & 7 & 7 & 6 & 6 & 1 & 6 & 6 & 6 & 1 & 6 & 6 & 6 & 6 & 1 & 6 & 6 & 6 & 1 & 6 & 6 & 6 & 6 & 1 & 6 & 6 & 8 & 6 & 8 & 2 & 8 & 8 & 1 & 1 & 4 & 4 & 4 & 3 & 2 & 3 & 2 & 3 & 3 & 3 & 0 & 99 & 99 & 0 & 77 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 77 & 3 & 2 & 4 & 1 & 8 & 8 & 8 & 4 & 1 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & 52 & \#¡NULO! & \#¡NULO! & 1 & \#¡NULO! & \#¡NULO! & 5 & \#¡NULO! & \#¡NULO! & 88 & \#¡NULO! & \#¡NULO! & 88 & 88 & \#¡NULO! & \#¡NULO! & 98 & \#¡NULO! & \#¡NULO! & 1 & 88 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 8 & 2 & 4 & 5 & 2 & 2 & 5 & 5 & 2 & 1 & 52 & 99 & 99 & 9999 & 99 & 99 & 2 & 1 & 5 & 99 & 99 & 1 & - & 6 & 2 & 88 & 1 & 3 & 0 & 99 & 0 & 99 & 99 & 99 & 3 & 7 & 3 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 2 & 2 & VICUÑA & 2 & 4 & 4 & 1 & 1 & 2.00 & 9.00 & 9.00 & 2.00 \\
4 & 1 & 1 & 1 & 10 & 8 & 1 & 6 & 10 & 4 & 1 & 4 & 4 & 1 & 1 & 1 & 1 & 1 & 1 & 7 & \#¡NULO! & 5 & 5 & 5 & \#¡NULO! & 2 & 3 & 5 & 6 & 4 & 5 & 1 & 4 & 4 & 4 & 4 & 4 & 4 & 1 & 1 & 4 & 3 & 4 & 4 & 4 & 1 & 4 & 4 & 1 & 2 & 3 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 1 & 1 & 1 & 10 & 4 & 4 & 10 & 4 & 3 & 3 & 3 & 1 & 3 & 3 & 3 & 3 & 4 & 4 & 4 & 6 & 6 & 6 & 6 & 6 & 6 & 4 & 10 & 2 & 2 & 5 & 2 & 1 & 1 & 1 & 999 & 999 & 2 & \#¡NULO! & \#¡NULO! & 38 & \#¡NULO! & \#¡NULO! & 4 & \#¡NULO! & \#¡NULO! & 6 & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & 1 & 5 & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & 7 & 7 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 9 & 8 & 2 & 1 & 5 & 2 & 5 & 2 & 1 & 1 & 1 & 1 & 2 & 3 & 4 & 2 & 1 & 5 & 2 & 2 & 3 & 2 & 1 & 59 & 13 & 1 & 1958 & 18 & 8 & 1 & 1 & 1 & 8 & 4 & 1 & - & 5 & 1 & 88 & 1 & 2 & 0 & 99 & 1 & 1 & 11 & 12 & 1 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 2 & 1 & 2 & 1 & 1 & 1 & 1 & 1 & 2 & 2 & 1 & 2 & PEDRO AGUIRRE CERDA & 2 & 5 & 13 & 1 & 1 & 2.00 & 1.00 & 4.00 & 1.00 \\
8 & 1 & 1 & 4 & 7 & 3 & 3 & 4 & 16 & 3 & 2 & 2 & 3 & 2 & 2 & 2 & 2 & 1 & 2 & 88 & 4 & 5 & 8 & 6 & 6 & 2 & 6 & 4 & 6 & 6 & 6 & 3 & 6 & 6 & 6 & 2 & 4 & 4 & 3 & 6 & 3 & 6 & 6 & 6 & 4 & 2 & 4 & 6 & 6 & 4 & 2 & 1 & 8 & 8 & 1 & 2 & 2 & 3 & 1 & 2 & 3 & 3 & 2 & 2 & 3 & 3 & 9 & 8 & 7 & 10 & 8 & 9 & 3 & 3 & 2 & 8 & 8 & 8 & 1 & 8 & 4 & 4 & 4 & 4 & 8 & 8 & 4 & 8 & 10 & 2 & 3 & 1 & 2 & 2 & 3 & 3 & 1 & 999 & 999 & 1 & \#¡NULO! & \#¡NULO! & 60 & \#¡NULO! & \#¡NULO! & 8 & \#¡NULO! & \#¡NULO! & 2 & \#¡NULO! & \#¡NULO! & 3 & \#¡NULO! & \#¡NULO! & 6 & 6 & \#¡NULO! & \#¡NULO! & 8 & \#¡NULO! & \#¡NULO! & 2 & 2 & \#¡NULO! & \#¡NULO! & 999 & 999 & 999 & 999 & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & \#¡NULO! & 8 & 2 & 4 & 2 & 8 & 8 & 4 & 2 & 4 & 2 & 2 & 4 & 2 & 2 & 1 & 2 & 2 & 3 & 2 & 2 & 2 & 2 & 1 & 59 & 3 & 8 & 1957 & 12 & 4 & 2 & 3 & 9 & 2 & 2 & 2 & - & 1 & 1 & 5 & 1 & 1 & 0 & 99 & 0 & 99 & 8 & 8 & 1 & 1 & 4 & 1 & 1 & 2 & 2 & 1 & 2 & 1 & 1 & 1 & 2 & 1 & 1 & 2 & 1 & 2 & 2 & 2 & 2 & 2 & TEMUCO & 2 & 5 & 9 & 1 & 1 & 3.00 & 2.00 & 3.00 & 2.00
\end{longtable}

```{r}
library(dlookr)      # for exploratory data analysis and imputation
plot_na_pareto(airquality, only_na = TRUE)
```

```{r}
plot_na_intersect(airquality)
```

```{r}
library(visdat)      # for visualizing NAs
library(plotly)      # for interactive visualization
vis_miss(airquality) %>% ggplotly()
```

```{r}
blip <- imputate_na(airquality, Ozone, Solar.R, method = "mean")
plot(blip)
```
```{r}
blip
```

\includegraphics[width=8cm, height=5cm]{logo1.png}
